A holomorphic approach to membranes and fivebranes

### 2022-06-29 fivebranes/twisted.tex
all around

Eleven-dimensional supergravity is the unique...
Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
\begin{itemize}
\item 
The minimal twist. 
This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
\item 
The non-minimal twist. 
This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
\end{itemize}

In this paper we will focus primarily on the minimal twist. 
In \cite{SWspinor} a complete description of the free limit of this twist of eleven-dimensional supergravity is given.
Within the BV formalism, the theory is only $\Z/2$ graded, a point we will elaborate on further soon. 
In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory in a background with global symmetry group $SU(5)$.
Globally, the eleven-dimensional theory exists on any manifold of the form $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.

@@

Deformations of the background metric which survive the twist can be identified with Beltrami differentials, that is, sections of 
\[
\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* 
\]
which we will denote by $\mu$. 
In local holomorphic coordinates $\mu$ admits a description like
\[
\mu = \mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_i} .
\]

One of the other bosonic fields of eleven-dimensional supergravity is a three-form which is usually denoted by~$C$. 
On $S \times X$ the space of complex-valued three-forms decomposes into de Rham--Dolbeault forms as in
\[
\oplus_{k+p+q=3} \Omega^k(S) \otimes \Omega^{p,q}(X) .
\]
We denote the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
\[
\sum_{P,Q} f_{PQ} (t;z,\zbar) \d z_P \d \zbar_Q + \sum_{P',Q'} g_{P'Q'}(t;z,\zbar) \d t \d z_{P'}\d \zbar_{Q'} 
\]
where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$ such that $\sum_i (p_i + q_i) = 3$, $0 \leq p_i,q_i \leq 3$.
The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.

@@

@@

The phase space is equipped with a natural symplectic form given by
\[
\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
\]
There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C \setminus 0$ which extends to zero. 
The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.

>>>>

Eleven-dimensional supergravity is the unique supersymmetric theory in eleven dimensions.
It plays an important role as the low energy limit of $M$ theory.

Recently in \cite{CLsugra}, Costello and Li gave a rigorous definition of twisted supergravity.
In any theory of supergravity, there is an collection of bosonic ghosts which, in part, incorporate local supersymmetry.
By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.

Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
\begin{itemize}
\item 
The minimal twist. 
This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
\item 
The non-minimal twist. 
This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
\end{itemize}

In this paper we will focus primarily on the minimal twist. 
In \cite{SWspinor} a complete description of the free limit of this twist of eleven-dimensional supergravity is given.
Within the BV formalism, the theory is only $\Z/2$ graded, a point we will elaborate on further soon. 
In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory in a background with global symmetry group $SU(5)$.
Globally, the eleven-dimensional theory exists on any manifold of the form 
\[
S \times X 
\] 
where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.

@@

Deformations of the background metric which survive the twist can be identified with Beltrami differentials, that is, sections of 
\[
\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* 
\]
which we will denote by $\mu$. 
In local holomorphic coordinates $\mu$ admits a description like
\[
\mu = \mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_i} .
\]
Part of the equations of motion for $\mu$ dictate that it be locally constant along~$S$.
Ordinarily, for $\mu$ to describe a deformation of complex structure in the $X$ direction we would require that it satisfy the Muarer--Cartan equation.
For twisted supergravity, however, we find a modification of this equation which involves the twisted analog of another familiar field.

One of the other bosonic fields of eleven-dimensional supergravity is a three-form that we denote by~$\sf C$. 
On $S \times X$ the space of complex-valued three-forms decomposes into de Rham--Dolbeault forms as in
\[
\oplus_{k+p+q=3} \Omega^k(S) \otimes \Omega^{p,q}(X) .
\]
We denote the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
\[
\sum_{P,Q} f_{PQ} (t;z,\zbar) \d z_P \d \zbar_Q + \sum_{P',Q'} g_{P'Q'}(t;z,\zbar) \d t \d z_{P'}\d \zbar_{Q'} 
\]
where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$ such that $\sum_i (p_i + q_i) = 3$, $0 \leq p_i,q_i \leq 3$.
The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.

@@

Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
Thus, locally we can assume that the $\Omega^1(S)$ components are exact and the $\Omega^0(S)$ components are locally constant.

@@

The phase space is equipped with a natural symplectic form given by
\[
\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
\]
There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero. 
The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.
